### 2023-01-18 paper.tex
Feedback for Section III

	However, the principal difference between optimizing conventional programs and smart contracts lies in the fact that smart contracts have to be optimized primarily in terms of the gas cost~\cite{superoptimization}. The smart contract code, when deployed on the Ethereum network, is compiled into \textit{bytecode}. The bytecode is a string made of concatenated op-codes that are executed in sequence when the smart contract is invoked~\cite{wood2019ethereum}. The execution of each opcode is associated with a certain energy consumption, which is calculated and charged from the user accoording to the EVM \textit{gas model} ~\cite{wood2019ethereum}. This means that optimizing and analyzing smart contracts need to be done not only at the level of the source code, but also at the corresponding bytecode. Optimizing smart contract code directly implies optimizing the gas cost through the bytecode. This introduces an additional constraint and hence requires techniques for constraint-optimized pattern recognition \cite{utilitypattern}.\todo{Since the current version of the repository does not provide the bytecode, do we really want to highlight it here. Also, again, there is a logical/storyline gap between this paragraph and the next one, which should be bridged.}

@@

	Ethereum was the first blockchain to introduce smart contracts and the high level language Solidity to program smart contracts in. Solidity has grown to be the most mature and popular programming language for smart contracts~\cite{soliditycheck}. A majority of the contracts available on GitHub is written for the Ethereum blockchain, in Solidity~\cite{empiricalgithubcontracts}\todo{I do not see that the referenced paper shows this.}, and hence, Solidity was the language of choice in preparing the dataset\todo{Since it is not described yet what the paper will deliver, the reader actually does NOT know what this ``dataset'' is referring to. If I just read this particular paragraph, I would think that only a dataset is delivered (what we do not do!).}.  The dataset is compiled by crawling through and scraping publicly accessible repositories on GitHub that have Solidity as the main language. The repositories are identified and all available commits of each file are downloaded using the GitHub API. Due to the varying licenses of GitHub repositories, the dataset is being distributed in the form of a Python script which can be run to scrape GitHub and prepare the dataset in an SQLite database. During experimentation, the script collected 163,961 files from 1021 repositories.\todo{I do not like this paragraph too much, since it mixes things up quite a lot. First, it tries to justify why Solidity is used, which is fine (however, better grounding in the literature is necessary). However, afterwards, there is a mixture of repository functionalities and outcomes in terms of the the collected files. Please separate these parts better; this shows also again that it is necessary to first clearly describe what this paper is going to deliver. On another note: I also do not think that the problem with the licenses is highlighted here in enough detail. It's actually mentioned only very very briefly. I do not know if this is taken up later on again, but from I read here, I would not understand (as a normal reader) why there is actually a need for the script at all.}

@@

	\subsection{Smart Contracts:}
	In the original Ethereum paper, Buterin described smart contracts as “systems which automatically move digital assets according to arbitrary pre-specified rules”\cite{ethpaper}. A smart contract is a program, that resides on the blockchain and is executed every time a user interacts with it. According to Dannen, smart contracts run business logic and enforce payment agreements between parties \cite{bitcoinbook}. Albert et al. have defined a smart contract from a more technical perspective as a collection of code (its functions) and data (its state) that resides at a specific address on the Ethereum blockchain \cite{gasol}.

@@

	A smart contract can be written in various high level languages, but is complied into bytecode when deployed on the blockchain. For example, Ethereum introduces the programming language called Solidity, which can used to write smart contracts which are then run on the Ethereum Virtual Machine (EVM). The EVM is a quasi-Turing complete machine \cite{wood2019ethereum} in that it restricts the over-utilisation of resources by limiting the \textit{gas cost}. Each transaction on the Ethereum network has an associated gas consumption, which has to be paid for by the initiator of the transaction. A smart contract is essentially a collection of operations that incur gas cost \cite{wood2019ethereum}. Hence the deployment and invocations of a smart contract have gas consumption associated with them.

@@

	\subsection{Code Mining:}
	Mining software repositories is the process of finding patterns by analyzing the large corpus of source code available in software repositories \cite{msrllm}. Such patterns depend on the type of end-analysis desired and can point to software development best practices, duplicated vulnerable code or optimizing constructs, among others.

	Code mining describes the process of automatic evaluation and optimization of software code. This is usually done with source code in a high level programming language, but it can also be done with low-level byte code. Good programming follows certain design principles that can be specific to the language that is used and the application that is built, but at the same time general rules apply to nearly all software projects. Violations of these design principles are called code smells \cite{codesmellmining}. One of the main purposes of code mining is to automatically detect and possibly remove code smells. Different algorithms can be used for code mining, depending on the optimizations that should be achieved.

@@

	To the best of our knowledge, the analysis of smart contract code has only gained relatively little attention by the research community so far. Nevertheless, there are a number of according approaches to the optimization of gas cost of smart contracts, which we discuss in the following.

	Notably, code smell detection and code optimization for conventional programs have been a very vivid field of research for many years~\cite{codesmellmining} and some of those concepts have trickled down to smart contracts. SmartDagger~\cite{smartdagger} is a tool which used static analysis of smart contract bytecode to detect cross-contract vulnerability. Manticore~\cite{manticore} is a tool that uses dynamic symbolic execution to test and detect flaws in source code. Existing program verification frameworks such as Boogie or LLVM can be used to perform formal verification of smart contracts~\cite{formalverification}.

	Brandstätter et al. \cite{brandstatter} explored optimization strategies to implement a rule-based Solidity source code optimizer. The authors conclude that automatic rule detection and optimization need to be extended. Chen et al. have published multiple papers regarding the gas cost optimization of smart contracts \cite{chen1devour, chen2gaschecker, chen3soda, chen4stan}. Starting in 2017, they were one of the first to address the problem of gas optimization. They identified seven antipatterns in Solidity bytecode and presented the tool GASPER to identify three of these gas-costly patterns \cite{chen1devour}. In 2018, they presented an in-depth investigation and the GasReducer tool, which can automatically check bytecode and run bytecode-to-bytecode optimization for 24 under-optimized code patterns. in 2020, the tools SODA \cite{chen3soda} and GasChecker~\cite{chen2gaschecker} followed, again dedicated to optimize byte code based on pre-defined rules and patterns.

	Nagele et al. presented the SuperOptimizer \textit{ebso} in 2020. Using techniques of a Satisfiability Modulo Theories (SMT) solver, they developed and tested a tool that could run EVM byte code optimizations \cite{nagele}. In 2017, Albert et al. presented EthIR, ``a framework for analyzing Ethereum bytecode'' \cite{ethir}. EthIR is an extension of OYENTE that was published by Luu et al. \cite{oyente}. OYENTE is a symbolic execution tool that works with smart contract bytecode and detects bugs for pre-deployment mitigation. It uses the Z3 theorem solver~\cite{z3solver} for symbolic execution of the smart contract code~\cite{oyente}. In 2020, Albert et al. introduced the Eclipse\footnote{Eclipse IDE: https://www.eclipse.org/ide/} plugin GASOL that allows the user to investigate and optimize their Solidity code with different cost models \cite{gasol}.

	Most of the published work in the field of optimization of smart contracts focus on the analysis of the compiled bytecode and on detecting similarities between the source code and predefined patterns that can indicate vulnerabilities and malicious constructs. There has been limited research on deriving those patterns from a automatically, which could lead to the automation of existing optimization possibilities while providing opportunities for previously undetected optimization patterns.  The existing attempts at automating the optimization of smart contracts mainly utilize static and dynamic analysis of the smart contract source code or bytecode. In 2022, Albert et al. published another tool called Syrup~\cite{superoptimization} that is aimed at optimizing smart contracts based on an analysis of the blocks in the Control Flow Graph. The tool breaks up each block into sub-blocks based on state modifying instructions and sends each sub-block to a Max-SMT solver such as Z3~\cite{z3solver} to obtain an optimized version of the sub-block~\cite{superoptimization}. Feist et al. published Slither, a framework for static analysis of smart contracts. Slither provides information regarding the performance, accuracy and robustness of smart contracts. However, the static analysis is less focused on the gas cost \cite{slither}. Di Angelo et al. released an investigation and listing of 27 different tools designed to analyze smart contracts \cite{diangelo}. They concluded that the research community was in need of an open source benchmark suite of smart contracts. Chunmiao Li proposed optimization techniques for smart contracts using machine learning and deep learning techniques to estimate the gas consumption of specific types of constructs, such as loops and storage manipulation~\cite{chunmiaoli}.

@@

	In the domain of repositories of smart contracts, Pierro et al. developed the Smart-Corpus software that creates a repository of verified smart contracts extracted from Etherscan and allows the download of and computation of metrics on the contracts in the repository~\cite{smartcorpus}. Other repositories, such as the ones by Ren et. al.~\cite{renrepo}, Ferreira et. al.~\cite{ferreirarepo} and SCRAWLD~\cite{scrawld} all contain deployed versions of smart contracts or synthetic smart contracts and do not have associated version histories. The repository presented in this paper is distinct and novel in that it includes metadata as well as the complete version history of each contract and is not limited to a particular use case. Thus this repository can prove useful to all use cases mentioned in this section.

	Apart from improving other smart contracts, a repository can also benefits researching conducting studies on contract design patterns. For example, Wöhrer et al. presented recommendations for the development of smart contracts closely connected to the money transferring fashion of smart contracts \cite{wohrer}. In 2020, Marchesi et al. presented 24 design patterns for smart contracts categorized based on their features \cite{marchesi}. While most of such studies are based on manual inspection of existing smart contracts, a corpus of smart contracts may be helpful in automating the detection of such patterns and potentially analyzing their effects on gas cost. Additionally, evaluating and designing new programming languages aimed at providing predictable gas consumption with efficient bytecode, requires a dataset of smart contracts.

	As mentioned in Section~\ref{sec:intro}, many applications developed for conventional code can be extended to smart contracts with training and evaluation on the proposed dataset.  Recommendation systems such as HelpMeOut~\cite{helpmeout}, ParseWeb~\cite{parseweb} and others can be trained to recommend snippets of Solidity code . Large Language Models focused on code, such as Codex \cite{codex} can be trained on the repository to work with smart contracts to add to its capabilities. In security research, apart from analysing individual deployed smart contracts, their version histories stored in the repository can be used to detect patterns that introduce or resolve vulnerabilities extending the work done in ~\cite{securitydataset}. Since the programming languages used in writing smart contracts are high level languages similar to conventional programming languages, most of the existing tools and research can be extended to smart contracts. A complete repository of source code is the first step in achieving that aim. Our repository aims to fill that gap and provide researchers with complete information regarding smart contract source code and their versions. This repository is different from the repository of smart contracts that can be obtained from existing APIs, such as those provided by Etherscan\footnote{https://etherscan.io/}, since such APIs can only provide a single version of a smart contract deployed on the blockchain.

>>>>

	However, the principal difference between optimizing conventional programs and smart contracts lies in the fact that smart contracts have to be optimized primarily in terms of the gas cost~\cite{superoptimization}. The smart contract code, when deployed on the Ethereum network, is compiled into \textit{bytecode}. The bytecode is a string made of concatenated op-codes that are executed in sequence when the smart contract is invoked~\cite{wood2019ethereum}. The execution of each opcode is associated with a certain energy consumption, which is calculated and charged from the user according to the EVM \textit{gas model} ~\cite{wood2019ethereum}. This means that optimizing and analyzing smart contracts need to be done not only at the level of the source code, but also at the corresponding bytecode. Optimizing smart contract code directly implies optimizing the gas cost through the bytecode. This introduces an additional constraint and hence requires techniques for constraint-optimized pattern recognition \cite{utilitypattern}.\todo{Since the current version of the repository does not provide the bytecode, do we really want to highlight it here. Also, again, there is a logical/storyline gap between this paragraph and the next one, which should be bridged.}

@@

	Ethereum was the first blockchain to introduce smart contracts and the high-level language Solidity to program smart contracts in. Solidity has grown to be the most mature and popular programming language for smart contracts~\cite{soliditycheck}. A majority of the contracts available on GitHub is written for the Ethereum blockchain, in Solidity~\cite{empiricalgithubcontracts}\todo{I do not see that the referenced paper shows this.}, and hence, Solidity was the language of choice in preparing the dataset\todo{Since it is not described yet what the paper will deliver, the reader actually does NOT know what this ``dataset'' is referring to. If I just read this particular paragraph, I would think that only a dataset is delivered (what we do not do!).}.  The dataset is compiled by crawling through and scraping publicly accessible repositories on GitHub that have Solidity as the main language. The repositories are identified and all available commits of each file are downloaded using the GitHub API. Due to the varying licenses of GitHub repositories, the dataset is being distributed in the form of a Python script which can be run to scrape GitHub and prepare the dataset in an SQLite database. During experimentation, the script collected 163,961 files from 1021 repositories.\todo{I do not like this paragraph too much, since it mixes things up quite a lot. First, it tries to justify why Solidity is used, which is fine (however, better grounding in the literature is necessary). However, afterwards, there is a mixture of repository functionalities and outcomes in terms of the the collected files. Please separate these parts better; this shows also again that it is necessary to first clearly describe what this paper is going to deliver. On another note: I also do not think that the problem with the licenses is highlighted here in enough detail. It's actually mentioned only very very briefly. I do not know if this is taken up later on again, but from I read here, I would not understand (as a normal reader) why there is actually a need for the script at all.}

@@

	\subsection{Smart Contracts}
	In the original Ethereum paper, Buterin described smart contracts as ``systems which automatically move digital assets according to arbitrary pre-specified rules''\todo{I've replaced the quotation marks, but please check how to set them properly in LaTeX (Actually, your IDE shoudl do that for you)}\cite{ethpaper}. A smart contract is a program, that resides on the blockchain and is executed every time a user interacts with it. According to Dannen, smart contracts run business logic and enforce payment agreements between parties \cite{bitcoinbook}. Albert et al. have defined a smart contract from a more technical perspective as a collection of code (its functions) and data (its state) that resides at a specific address on the Ethereum blockchain \cite{gasol}.

@@

	A smart contract can be written in various high-level languages, but is complied into bytecode when deployed on the blockchain. For example, Ethereum introduces the programming language called Solidity, which can used to write smart contracts which are then run on the Ethereum Virtual Machine (EVM). The EVM is a quasi-Turing complete machine \cite{wood2019ethereum} in that it restricts the over-utilisation of resources by limiting the \textit{gas cost}. Each transaction on the Ethereum network has an associated gas consumption, which has to be paid for by the initiator of the transaction. A smart contract is essentially a collection of operations that incur gas cost \cite{wood2019ethereum}. Hence the deployment and invocations of a smart contract have gas consumption associated with them.

@@

	\subsection{Code Mining}
	Mining software repositories is the process of finding patterns by analyzing the large corpus of source code available in software repositories \cite{msrllm}. Such patterns depend on the type of end-analysis desired and can point to software development best practices, duplicated vulnerable code or optimizing constructs, among others.

	Code mining describes the process of automatic evaluation and optimization of software code. This is usually done with source code in a high-level programming language, but it can also be done with low-level bytecode. Good programming follows certain design principles that can be specific to the language that is used and the application that is built, but at the same time general rules apply to nearly all software projects. Violations of these design principles are called code smells \cite{codesmellmining}. One of the main purposes of code mining is to automatically detect and possibly remove code smells. Different algorithms can be used for code mining, depending on the optimizations that should be achieved.

@@

	To the best of our knowledge, the analysis of smart contract code has only gained relatively little attention by the research community so far. Nevertheless, there are a number of according approaches for the optimization of gas cost of smart contracts, which we discuss in the following.

	Notably, code smell detection and code optimization for conventional programs have been a very vivid field of research for many years~\cite{codesmellmining} and some of those concepts have trickled down to smart contracts. SmartDagger~\cite{smartdagger} is a tool which uses static analysis of smart contract bytecode to detect cross-contract vulnerability. Manticore~\cite{manticore} is a tool that uses dynamic symbolic execution to test and detect flaws in source code. Existing program verification frameworks such as Boogie or LLVM can be used to perform formal verification of smart contracts~\cite{formalverification}.

	Brandstätter et al. \cite{brandstatter} explored optimization strategies to implement a rule-based Solidity source code optimizer. The authors conclude that automatic rule detection and optimization need to be extended. Chen et al. have published multiple papers regarding the gas cost optimization of smart contracts \cite{chen1devour, chen2gaschecker, chen3soda, chen4stan}. Starting in 2017, they were one of the first to address the problem of gas optimization. They identified seven antipatterns in Solidity bytecode and presented the tool GASPER to identify three of these gas-costly patterns~\cite{chen1devour}. In 2018, they presented an in-depth investigation and the GasReducer tool, which can automatically check bytecode and run bytecode-to-bytecode optimization for 24 under-optimized code patterns. In 2020, the tools SODA \cite{chen3soda} and GasChecker~\cite{chen2gaschecker} followed, again dedicated to optimize bytecode based on pre-defined rules and patterns.

	Nagele et al. presented the SuperOptimizer \textit{ebso} in 2020. Using techniques of a Satisfiability Modulo Theories (SMT) solver, they developed and tested a tool that can run EVM bytecode optimizations \cite{nagele}. In 2017\todo{As written before, rather do not provide any years/dates in the running text. The exception is the work by Chen et al., since this tells a nice story.. I would not do that for Albert et al., even though they also have two papers. }, Albert et al. presented EthIR, ``a framework for analyzing Ethereum bytecode'' \cite{ethir}. EthIR is an extension of OYENTE that was published by Luu et al. \cite{oyente}. OYENTE is a symbolic execution tool that works with smart contract bytecode and detects bugs for pre-deployment mitigation. It uses the Z3 theorem solver~\cite{z3solver} for symbolic execution of the smart contract code~\cite{oyente}. In 2020, Albert et al. introduced the Eclipse\footnote{Eclipse IDE: https://www.eclipse.org/ide/} plugin GASOL that allows the user to investigate and optimize their Solidity code with different cost models \cite{gasol}.

	Most of the published work in the field of optimization of smart contracts focus on the analysis of the compiled bytecode and on detecting similarities between the source code and predefined patterns that can indicate vulnerabilities and malicious constructs. There has been limited research on deriving those patterns from a\todo{Something is wrong here} automatically, which could lead to the automation of existing optimization possibilities while providing opportunities for previously undetected optimization patterns.  Instead, the existing attempts at automating the optimization of smart contracts mainly utilize static and dynamic analysis of the smart contract source code or bytecode\todo{Is this sentence really necessary? It sounds like a little bit of a repetition}.\todo{Logical gap here again: Why is the third paper from Albert et al. mentioned here? The framing is not really good. Or should there be a paragraph before starting with the dicussion of the third Albert et al. paper?} In 2022, Albert et al. published another tool called Syrup~\cite{superoptimization} that is aimed at optimizing smart contracts based on an analysis of the blocks in the Control Flow Graph. The tool breaks up each block into sub-blocks based on state-modifying instructions and sends each sub-block to a Max-SMT solver such as Z3~\cite{z3solver} to obtain an optimized version of the sub-block~\cite{superoptimization}. Feist et al. published Slither, a framework for static analysis of smart contracts. Slither provides information regarding the performance, accuracy and robustness of smart contracts. However, the static analysis is less focused on the gas cost~\cite{slither}. Di Angelo et al. released an investigation and listing of 27 different tools designed to analyze smart contracts \cite{diangelo}. They concluded that the research community was in need of an open source benchmark suite of smart contracts. Chunmiao Li proposed optimization techniques for smart contracts using machine learning and deep learning techniques to estimate the gas consumption of specific types of constructs, such as loops and storage manipulation~\cite{chunmiaoli}.

@@

	In the domain of repositories of smart contracts, Pierro et al. developed the Smart-Corpus software that creates a repository of verified smart contracts extracted from Etherscan and allows the download of and computation of metrics on the contracts in the repository~\cite{smartcorpus}. Other repositories, such as the ones by Ren et. al.~\cite{renrepo}, Ferreira et. al.~\cite{ferreirarepo} and SCRAWLD~\cite{scrawld} all contain deployed versions of smart contracts or synthetic smart contracts and do not have associated version histories. The Smart Contract Repository presented in this paper is distinct and novel in that it includes metadata as well as the complete version history of each contract and is not limited to a particular use case. Thus, this repository can prove useful to all use cases mentioned in this section.

	Apart from improving other smart contracts, a repository can also benefits researching conducting\todo{''researching conducting''? Is this correct?} studies on contract design patterns. For example, Wöhrer et al. presented recommendations for the development of smart contracts closely connected to the money transferring fashion of smart contracts~\cite{wohrer}. In 2020\todo{Again, please get rid of the years. This is never done.}, Marchesi et al. presented 24 design patterns for smart contracts categorized based on their features \cite{marchesi}. While most of such studies are based on manual inspection of existing smart contracts, a corpus of smart contracts may be helpful in automating the detection of such patterns and potentially analyzing their effects on gas cost. Additionally, evaluating and designing new programming languages aimed at providing predictable gas consumption with efficient bytecode, requires a dataset of smart contracts\todo{The final sentence is for sure correct, but do you have a reference for this?}.

	As mentioned in Section~\ref{sec:intro}, many applications developed for conventional code can be extended to smart contracts with training and evaluation on the proposed dataset.  Recommendation systems such as HelpMeOut~\cite{helpmeout}, ParseWeb~\cite{parseweb} and others could be trained to recommend snippets of Solidity code. LLMs focused on code, such as Codex \cite{codex} could be trained on the repository to work with smart contracts to add to its capabilities. In security research, apart from analysing individual deployed smart contracts, their version histories stored in the repository could be used to detect patterns that introduce or resolve vulnerabilities extending the work done, e.g., in~\cite{securitydataset}. Since the programming languages used in writing smart contracts are high-level languages similar to conventional programming languages, most of the existing tools and research can be extended to smart contracts. A complete repository of source code is the first step in achieving that aim. Our repository aims to fill that gap and provide researchers with complete information regarding smart contract source code and their versions. This repository is different from the repository of smart contracts that can be obtained from existing APIs, such as those provided by Etherscan\footnote{https://etherscan.io/}, since such APIs can only provide a single version of a smart contract deployed on the blockchain.
	\todo{The RW section is in general well-written, but there are some unwanted repetitions. For instance, you should discuss the weaknesses of Etherscan when it is mentioned the first time. Not start discussing it, then do something else, then go back to Etherscan. This is just one example - paper text should have also a high cohesion and loose coupling, just like code.}
